---
title: "springboard capstone"
author: "milti leonard"
date: "7/9/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Detecting Bot Communities on Twitter and Determining Their Influence

Social media commands a tremendous influence on the ongoing zeitgeist, at times to the point of crafting and shaping it. This influence can have IRL (or real world) consequences and repercussions. The intent of the platform is to allow people of various backgrounds, but similar interests, to connect and form communities of the like-minded that is not limited by geospatial constraints. However, the reality is that various agents create and unleash *bot* accounts that disrupt those communities and alters the digital landscape making it at times a dark and hostile place.

This project will focus on a selected single *loaded* hashtag (meaning one whose LIWC is representative of a defined agenda) that command a respectable trending status to see whether or no it attracts these *bot* accounts and to what degree. Also to be investigated, is whether it is the human accounts or their *bot* counterparts that take the lead in establishing that trending status. I'm using as a roadmap Erin Shellman's class assignment on classifying whether a Twitter account is a bot or not, the problem statement (as well as a description of the dataset) can be found here, https://github.com/erinshellman/BI-TECH-CP303/blob/master/projects/project%202/problem_statement_project_2.md.

That project did not involve (nor describe) the gathering and ETL of the dataset presented to her students. The package I used to gather tweets to shape my dataset is as follows:

1. I leveraged another college project to first gather Twitter accounts denoted to be bots, *Debot*, found here, https://github.com/nchavoshi/debot_api. Using an API key I selected my *hashtag* ("Charlottesville) and collected a set of tweets that had used the *hashtag* and were determined (by this program) to be from *bot* accounts. This set included whether or no the *tweet* was a *retweet*, a *reply* or an original *tweet*. 

```{r, set-options, eval=FALSE, cache=FALSE}

library(reticulate)
library(XML)
#path_to_python <- "/usr/local/bin/python3.6"
path_to_python <- "/Library/Frameworks/Python.framework/Versions/3.6/bin/python3.6"
use_python(path_to_python)
dbot=import("debot")
db = dbot$DeBot('YocR3mKAc7U6hjKZrNnOCk2jjnWrqgSfwWYo8yOb')#This is my API key
cbots=htmlParse(db$get_related_bots('Charlottesville'))


#Now parse the XML data into a list of screennames or accounts.
botlist <- xmlToList(cbots)

library(listviewer)
flatbot <- flatten(botlist)
flatterbot <- flatten(flatbot)
remove(flatbot)
flatbot <- flatten(flatterbot)
newBotlist <- unname(sapply(flatbot, `[`, 2))

```

The *newBotlist* object is a nested list of 646 names:

R >  head(str(newBotlist)) 
List of 646
 $ : chr "15_margiecastro"
 $ : chr "2001shaira"
 $ : chr "78fb1da7564c40c"
 $ : chr "AaaRDieeee"
 ....
 
 
2. Utilising the _twitteR_ package, I used the extracted account names from the group of tweets gathered from *Debot* step and gathered information on the accounts themselves, such as when the account was created and the number of tweets thus far.


```{r, set-options, eval=FALSE, cache=FALSE}

library(twitteR)
library(ROAuth)


requestURL <- "https://api.twitter.com/oauth/request_token"
accessURL <- "https://api.twitter.com/oauth/access_token"
authURL <- "https://api.twitter.com/oauth/authorize"
consumerKey <- "gI20zgelMl60fP7KE3GWtHTBl"
consumerSecret <- "hZDUuFonXapqeO0puVSV2RyaqJmMCziDRXKWOg0RldL135LHy4"
accessToken <- "1240280636-PTXARRUrytYtijYXyPWKptD9cHSCMzlAujQkATI"
accessTokenSecret <- "uo8INEJbhhe43AIXfSs5veSZ6i7IHbh8Tn1LLlYTJqOm2"
handle <- "conjja"

setup_twitter_oauth(consumerKey, consumerSecret, accessToken, accessTokenSecret)

botAccts <- lookupUsers(newBotlist)
## or just load the dataset: > botAccts <- load("capstone dataset/botAccts")

botAcctlist <- twListToDF(botAccts)
acctNames <- row.names.data.frame(botAcctlist)

```

The resulting dataframe was educed to 352 observations:

R >  str(botAcctlist)
'data.frame':	352 obs. of  17 variables:

Those variables are:

R >  names(botAcctlist)
 [1] "description"       "statusesCount"     "followersCount"    "favoritesCount"   
 [5] "friendsCount"      "url"               "name"              "created"          
 [9] "protected"         "verified"          "screenName"        "location"         
[13] "lang"              "id"                "listedCount"       "followRequestSent"
[17] "profileImageUrl"

We can see that several of the variables for the goal dataset are already in place: statusesCount, followersCount, etc. We're missing several variables listed in the Schellman's problem state referenced above. For convenience, let's list them here:

'data.frame':	3176 obs. of  15 variables:
 $ bot                     : int  0 0 0 0 0 0 0 0 0 0 ...
 $ statuses_count          : int  428 6239 80 12 4052 28 21 1379 2212 162 ...
 $ default_profile         : int  1 0 1 1 0 1 1 0 0 0 ...
 $ default_profile_image   : int  0 0 0 1 0 0 0 0 0 0 ...
 $ friends_count           : int  1867 896 161 1103 372 285 1555 291 2517 163 ...
 $ followers_count         : int  1680 372 54 140 387 31 192 184 3621 105 ...
 $ favourites_count        : int  0 4325 16 1 1751 0 15 188 212 340 ...
 $ geo_enabled             : int  0 1 0 0 1 0 1 0 1 0 ...
 $ listed_count            : int  29 4 15 1 21 1 0 9 145 6 ...
 $ account_age_hours       : int  3002 67482 23406 3676 14718 4898 2218 48548 57005 47479 ...
 $ diversity               : num  0.269 0.691 0.797 0.777 0.72 ...
 $ mean_mins_between_tweets: num  182 442 22847 4311 290 ...
 $ mean_tweet_length       : num  76 69.6 113.9 59.4 86.7 ...
 $ mean_retweets           : num  1.58 1.2 1.33 1 2.5 ...
 $ reply_rate              : num  0 0.2455 0.0492 0.5312 0.4419 ...



3. I then took the same accounts and gathered 200 of the most recent tweets (or as many as I could retrieve) from those accounts to get enough messaging to test the account's linguistic diversity.


```{r, set-options, eval=FALSE, cache=FALSE}

library(stringr)

recentTweetsDS <- map(unlistedBots[], ~searchTwitteR(.x, resultType = "recent", n=200))
recentTweetsDF <- twListToDF(flatten(recentTweetsDS))
AppURL <- rm_between_multiple(recentTweetsDF$statusSource,"<",">")
recentTweetsDF$App <- unlist(AppURL)
appcount <- recentTweetsDF%>%group_by(App)%>%summarize(Count=n())%>%arrange(desc(Count))
recentTweetsDF <- left_join(recentTweetsDF,appcount)
recentTweetsDF$BoN <- ifelse(recentTweetsDF$Count>4,0,1)
shredDF <- recentTweetsDF %>% select(screenName, AppURL, App, Count, BoN)
#shredDF <- recentTweetsDF %>% select(screenName, App, Count, BoN)

```

4. A new dataframe was created to contain the variables that we will consider interesting. Then in order to truly test the linguistic diversity of the account, it's important to separate the *tweets* from the *retweets*.

```{r, set-options, eval=FALSE, cache=FALSE}
botDS <- data.frame(botAcctlist$screenName, botAcctlist$id, botAcctlist$created, botAcctlist$statusesCount, langDiv = 0, mean_time_betwn_tweets = 0, bot = 0)
columnnames <- names(botDS)
columnnames[1] <- "screenName"
columnnames[2] <- "ID"
columnnames[3] <- "acct_created"
columnnames[4] <- "statusesCount"
colnames(botDS) <- columnnames

tweetsRT <- filter(recentTweetsDF, isRetweet == "TRUE")
tweetsOPEN <- filter(recentTweetsDF, isRetweet != "TRUE")
#tweeters <- unique(tweetsOPEN$screenName)
#length(tweeters)

botDS <- left_join(botDS, shredDF, by = "screenName")

botDS <- botDS[, c(1, 6, 14, 16, 15, 18, 3, 12, 13, 4, 7, 9, 5, 8, 10, 11)]


groupedTweetsDF <- tweetsOPEN %>%
  group_by(screenName) %>%
  filter(screenName %in% botDS$screenName)
castoffDF <- setdiff(tweetsOPEN, groupedTweetsDF)

#binning the account creation column
table(cut(botDS$acct_created, breaks = "6 month"))


```
Binning the creation times of these accounts doesn't uncover anything that interesting. Although, the 6 month period with the highest number, "2015-09-01", was in the months following DJT declaring himslef a candidate for the GOP nomination. Changing the size of the time bins, also highlights that the peak of account creation (for this set of suspected accounts) also have a noticeable peak immediately surrounding the time following the announcement.

The R packages that will be utilised in this study are as follows (with one or two being dropped, dependent on subsequent decisions made in the experimental design)

5. In this step, the linguistic diversity of the account is tested by taking the original *tweets* and averaging the 

```{r, set-options, eval=FALSE, cache=FALSE}
library(quanteda)

#using quanteda pkg
langDiv <- textstat_lexdiv(dfm(groupedTweetsDF$text))

botDiv <- groupedTweetsDF %>%
  group_by(screenName) %>%
  summarise(meanDiv = rowMeans(langDiv[,-1]))

botDS <- left_join(botDS, botDiv)
botDS$langDiv <- botDS$meanDiv
#remove the meanDiv column for cleanup

#recreate latestStatDF code here where i get the latest statuses count for accounts to do mean_time_between_tweets variable
accts <- unlist(botDS$screenName)
#latestStat <- lookupUsers(accts)
latestStatDF <- twListToDF(lookupUsers(accts))

botDS$acct_age <- abs(as.numeric(botDS$acct_age, units = "mins"))
botDS <- left_join(botDS, latestStatDF[, c("screenName", "statusesCount")], by = "screenName")

botDS$mean_time_betwn_tweets = botDS$acct_age/botDS$statusesCount #time measured in minutes

```

Now, using _rtweet_, I've scraped some tweets using the same *hashtag*, #Charlottesville, without regard as to any supposition that the accounts likely be a *bot*. The resulting *twitter* tibble is trasnformed as follows:

```{r, set-options, eval=FALSE, cache=FALSE}

library(rtweet)

CTV <- search_tweets(
"#Charlottesville", n = 18000, include_rts = FALSE
)
ts_plot(CTV)

#get some LISC values for the tweets (or CTV$text)

divLang <- as.data.frame(textstat_lexdiv(dfm(CTV$text)))
divLang[mapply(is.infinite, divLang)] <- NA
divLang[mapply(is.nan, divLang)] <- NA
divMeans <- rowMeans(divLang, na.rm = TRUE)

CTV$langDiv <- divMeans

#start compiling the interim dataframe with values desired for ETL

ctvDS <- data.frame(CTV$screen_name, CTV$bot, CTV$acct_created, "julianCreated", "acct_age", CTV$langDiv, "Count", "mean_time_betwn_tweets", "App", "App.BoN", "mCount", "Month")

ctvnames <- names(ctvDS)
ctvnames[1] <- "screenName"
ctvnames[2] <- "bot"
ctvnames[3] <- "acct_created"
ctvnames[4] <- "julianCreated"
ctvnames[5] <- "acct_age"
ctvnames[6] <- "langDiv"
ctvnames[7] <- "Count"
ctvnames[8] <- "mean_time_betwn_tweets"
ctvnames[9] <- "App"
ctvnames[10] <- "App.BoN"
ctvnames[11] <- "mCount"
ctvnames[12] <- "Month"
ctvDS$acct_age <- abs(as.numeric(ctvDS$acct_age, units = "mins"))
colnames(ctvDS)
colnames(ctvDS) <- ctvnames

#perform a lookup of the user data in CTV 
CTVstats <- users_data(CTV)
names(CTVstats)

#use those variables in CTVstats that will be needed in the final dataframe

CTVsub <- CTVstats[, c(3, 8:11, 21)]
CTVbnd <- bind_cols(ctvDS, CTVsub)
#check that the bind worked as desired
CTVbnd %>% filter(CTVbnd$screenName != CTVbnd$screen_name)
CTVbnd %>% filter(CTVbnd$acct_created != CTVbnd$acct_created1)

#now create the final dataframe for this set of accounts of possible human origin

shredCTV <- CTVbnd[, c(1:12, 13, 14:17)]

#get the order of the columns for both DFs

names(botDS)
names(shredCTV)

#correct and set order for shredCTV in anticipation of combining them for the final dataframe for determining *bot or not*.

shredCTV <- shredCTV[, c(1,2,16,14,13,15,3,4,5,6,7,8,9,10,11,12)]
names(shredCTV)
names(botDS)
botDS <- botDS[,-11]
names(botDS)
names(shredCTV)
botnames <- names(botDS)
colnames(shredCTV)
colnames(shredCTV) <- botnames
names(shredCTV)
names(botDS)


shredCTV$mean_time_betwn_tweets = as.integer(shredCTV$acct_age/shredCTV$statusesCount)

#determine if some accounts use more than one method to tweet

methodCountCTV <- shredCTV %>% group_by(screenName, App) %>% summarise(count=n())
shredCTV <- left_join(shredCTV, methodCountCTV, by = c("screenName", "App"))
xn <- methodCountCTV %>% group_by(screenName) %>% summarise(mCount = n()) 
names(shredCTV)
shredCTV <- shredCTV[,-15]
shredCTV <- left_join(shredCTV, xn[,c("screenName", "mCount")], by = "screenName")
names(shredCTV)

#using the number of times the App is used in this set, arbitrate the likelihood that the account uses a *bot* application

shredCTV$App.BoN <- ifelse(shredCTV$Count >4,0,1)


# shredCTV <- shredCTV[, c(1,2,16,14,13,15,3,4,5,6,7,8,9,10,11,12)]

#combine botDS and shredCTV

shredCVL <- bind_rows(botDS, shredCTV)

#lets take an intital look.
summary(shredCVL)
```

R >  summary(shredCVL)
  screenName             bot    statusesCount      friendsCount   followersCount   
 Length:2618        Min.   :0   Min.   :      0   Min.   :    0   Min.   :      0  
 Class :character   1st Qu.:0   1st Qu.:   2524   1st Qu.:  258   1st Qu.:    277  
 Mode  :character   Median :0   Median :  13042   Median :  661   Median :    915  
                    Mean   :0   Mean   :  45605   Mean   : 1683   Mean   :  10366  
                    3rd Qu.:0   3rd Qu.:  41709   3rd Qu.: 1678   3rd Qu.:   2296  
                    Max.   :0   Max.   :1742257   Max.   :68232   Max.   :6604309  
                                NA's   :29        NA's   :29      NA's   :29       
  listedCount     acct_created                 julianCreated        acct_age      
 Min.   :    0   Min.   :2007-02-08 04:24:56   Length:2618       Min.   :   1361  
 1st Qu.:    4   1st Qu.:2010-04-16 14:56:21   Class :difftime   1st Qu.: 766986  
 Median :   22   Median :2012-09-06 16:14:22   Mode  :numeric    Median :2275666  
 Mean   :  143   Mean   :2012-11-08 23:14:03                     Mean   :2221613  
 3rd Qu.:  104   3rd Qu.:2015-07-21 08:54:27                     3rd Qu.:3534304  
 Max.   :39981   Max.   :2017-12-11 13:58:41                     Max.   :5209655  
 NA's   :29                                                                       
    langDiv      mean_time_betwn_tweets     App                Count     
 Min.   : 0.39   Min.   :      0        Length:2618        Min.   :   1  
 1st Qu.: 2.95   1st Qu.:     40        Class :character   1st Qu.:  62  
 Median : 5.57   Median :    127        Mode  :character   Median : 412  
 Mean   : 5.59   Mean   :  12156                           Mean   : 772  
 3rd Qu.: 7.50   3rd Qu.:    549                           3rd Qu.: 657  
 Max.   :29.07   Max.   :3598898                           Max.   :6238  
 NA's   :193     NA's   :38                                NA's   :164   
    App.BoN         mCount    
 Min.   :0.00   Min.   :1.00  
 1st Qu.:0.00   1st Qu.:1.00  
 Median :0.00   Median :1.00  
 Mean   :0.03   Mean   :1.29  
 3rd Qu.:0.00   3rd Qu.:1.00  
 Max.   :1.00   Max.   :4.00  
 NA's   :164                  
                
```{r, set-options, eval=FALSE, cache=FALSE}

#now let's look at the same set without the character and *difftime* variables

summary(shredCVL[, c(-1, -5)])
```

R >  summary(shredCVL[, c(-1, -5)])
      bot    statusesCount      friendsCount    listedCount   
 Min.   :0   Min.   :      0   Min.   :    0   Min.   :    0  
 1st Qu.:0   1st Qu.:   2524   1st Qu.:  258   1st Qu.:    4  
 Median :0   Median :  13042   Median :  661   Median :   22  
 Mean   :0   Mean   :  45605   Mean   : 1683   Mean   :  143  
 3rd Qu.:0   3rd Qu.:  41709   3rd Qu.: 1678   3rd Qu.:  104  
 Max.   :0   Max.   :1742257   Max.   :68232   Max.   :39981  
             NA's   :29        NA's   :29      NA's   :29     
  acct_created                 julianCreated        acct_age          langDiv     
 Min.   :2007-02-08 04:24:56   Length:2618       Min.   :   1361   Min.   : 0.39  
 1st Qu.:2010-04-16 14:56:21   Class :difftime   1st Qu.: 766986   1st Qu.: 2.95  
 Median :2012-09-06 16:14:22   Mode  :numeric    Median :2275666   Median : 5.57  
 Mean   :2012-11-08 23:14:03                     Mean   :2221613   Mean   : 5.59  
 3rd Qu.:2015-07-21 08:54:27                     3rd Qu.:3534304   3rd Qu.: 7.50  
 Max.   :2017-12-11 13:58:41                     Max.   :5209655   Max.   :29.07  
                                                                   NA's   :193    
 mean_time_betwn_tweets     App                Count         App.BoN    
 Min.   :      0        Length:2618        Min.   :   1   Min.   :0.00  
 1st Qu.:     40        Class :character   1st Qu.:  62   1st Qu.:0.00  
 Median :    127        Mode  :character   Median : 412   Median :0.00  
 Mean   :  12156                           Mean   : 772   Mean   :0.03  
 3rd Qu.:    549                           3rd Qu.: 657   3rd Qu.:0.00  
 Max.   :3598898                           Max.   :6238   Max.   :1.00  
 NA's   :38                                NA's   :164    NA's   :164   
     mCount    
 Min.   :1.00  
 1st Qu.:1.00  
 Median :1.00  
 Mean   :1.29  
 3rd Qu.:1.00  
 Max.   :4.00  
               
                
There are a couple of factor variables above that are not classed as such. Let's do so now.

```{r, set-options, eval=FALSE, cache=FALSE}

shredCVL$bot <- factor(shredCVL$bot)
shredCVL$App.BoN <- factor(shredCVL$App.BoN)


summary(shredCVL[, -c(1, 7, 8, 12)])
```
R >  summary(shredCVL[, -c(1, 7, 8, 12)])
 bot      statusesCount      friendsCount   followersCount     listedCount   
 0:2618   Min.   :      0   Min.   :    0   Min.   :      0   Min.   :    0  
          1st Qu.:   2524   1st Qu.:  258   1st Qu.:    277   1st Qu.:    4  
          Median :  13042   Median :  661   Median :    915   Median :   22  
          Mean   :  45605   Mean   : 1683   Mean   :  10366   Mean   :  143  
          3rd Qu.:  41709   3rd Qu.: 1678   3rd Qu.:   2296   3rd Qu.:  104  
          Max.   :1742257   Max.   :68232   Max.   :6604309   Max.   :39981  
          NA's   :29        NA's   :29      NA's   :29        NA's   :29     
    acct_age          langDiv      mean_time_betwn_tweets     Count      App.BoN    
 Min.   :   1361   Min.   : 0.39   Min.   :      0        Min.   :   1   0   :2377  
 1st Qu.: 766986   1st Qu.: 2.95   1st Qu.:     40        1st Qu.:  62   1   :  77  
 Median :2275666   Median : 5.57   Median :    127        Median : 412   NA's: 164  
 Mean   :2221613   Mean   : 5.59   Mean   :  12156        Mean   : 772              
 3rd Qu.:3534304   3rd Qu.: 7.50   3rd Qu.:    549        3rd Qu.: 657              
 Max.   :5209655   Max.   :29.07   Max.   :3598898        Max.   :6238              
                   NA's   :193     NA's   :38             NA's   :164               
     mCount    
 Min.   :1.00  
 1st Qu.:1.00  
 Median :1.00  
 Mean   :1.29  
 3rd Qu.:1.00  
 Max.   :4.00   

in_train <- createDataPartition(y = shredCVL$bot, p = .75, list = FALSE)
training_set <- shredCVL[in_train,]
testing_set <- shredCVL[-in_train,]


```{r, eval=FALSE}
#getting the source of the tweet (phone, web, other)
uniqSource <- unique(recentTweetsDF$statusSource)
inD <- which(str_detect(recentTweetsDF$statusSource, "Android"))
androidTweetsDF <- recentTweetsDF[inD,]

inD <- which(str_detect(recentTweetsDF$statusSource, "iP"))
iTweetsDF <- recentTweetsDF[inD,]

inD <- which(str_detect(recentTweetsDF$statusSource, "Web"))
webTweetsDF <- recentTweetsDF[inD,]

inD <- which(str_detect(recentTweetsDF$statusSource, paste(c("Android", "iP", "Web"), collapse = '|')))
otherTweetsDF <- recentTweetsDF[-inD,]

```

